ODGI: understanding pangenome graphs

### 2022-04-01 manuscript/main.tex
correct subsection numbering
nice to PAV you
split out supplement
remove red
fix affiliations

\newcommand{\vocab}{\textbf}
\newcommand{\red}[1]{{\textcolor{Red}{#1}}}
\newcommand{\FIXME}[1]{\red{[FIXME: #1]}}
\newcommand{\REVIEWED}[1]{{\textcolor{Red}{#1}}}
\newcommand{\beginsupplement}{%
	\setcounter{table}{0}
	\renewcommand{\thetable}{S\arabic{table}}%
	\setcounter{figure}{0}
	\renewcommand{\thefigure}{S\arabic{figure}}%
}

@@

\address{
$^{\text{\sf 1}}$Genomics Research Centre, Human Technopole, Milan, Italy \\
$^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, Germany, 72076 \\
$^{\text{\sf 3}}$Biomedical Data Science, Dept. of Computer Science, University of T\"ubingen, T\"ubingen, Germany, 72076 \\
$^{\text{\sf 4}}$University of Tennessee Health Science Center, Memphis, TN, USA
}

@@

%\FIXME{Update the references to the sections.}
\begin{itemize}
\item~\textit{odgi build} constructs the ODGI data model from GFA file (\S\ref{sec:build}).
\item~\textit{odgi view} converts the ODGI data model into GFA file (\S\ref{sec:build}).
\item~\textit{odgi viz} provides a linear visualization of the graph (\S\ref{sec:viz}).
\item~\textit{odgi draw} renders a 2D image of the graph (\S\ref{sec:viz}).
\item~\textit{odgi extract} excerpts subsets of the graph based on path ranges (\S\ref{sec:supp_edit}).
\item~\textit{odgi explode} breaks the graph into connected components (\S\ref{sec:supp_edit}).
\item~\textit{odgi squeeze} unifies disjoint graphs (\S\ref{sec:supp_edit}).
\item~\textit{odgi chop} breaks long nodes into shorter ones (\S\ref{sec:supp_edit}).
\item~\textit{odgi unchop} combines unitig nodes (\S\ref{sec:supp_edit}).
\item~\textit{odgi break} removes cycles in the graph (\S\ref{sec:supp_edit}).
\item~\textit{odgi prune} removes complex regions (\S\ref{sec:supp_edit}).
\item~\textit{odgi groom} resolves spurious inverting links (\S\ref{sec:supp_edit}).
\item~\textit{odgi position} lifts coordinates between path and graph positions (\S\ref{sec:untangle}).%
%\item \textit{odgi server} provides a HTTP server to lift coordinates (\S\ref{sec:untangle}).
\item~\textit{odgi untangle} deconvolutes paths relative to a reference (\S\ref{sec:untangle}).
\item~\textit{odgi tips} finds path end points relative to a reference (\S\ref{sec:supp_navigation}).
\item~\textit{odgi sort} orders the graph nodes (\S\ref{sec:sort}).
\item~\textit{odgi layout} establishes a 2D layout (\S\ref{sec:sort}).
\item~\textit{odgi matrix} derives the pangenome matrix (\S\ref{sec:supp_metrics}).
\item~\textit{odgi paths} lists and extracts paths in FASTA (\S\ref{sec:supp_metrics}).
\item~\textit{odgi flatten} converts the graph to FASTA and BED (\S\ref{sec:supp_metrics}).
\REVIEWED{\item~\textit{odgi pav} generates a presence-abscence variation table (\S\ref{sec:supp_pav}).}
\item~\textit{odgi stats} provides numerical properties of the graph (\S\ref{sec:metrics}).
\item~\textit{odgi bin} generates a summarized view of the graph (\S\ref{sec:supp_metrics}).
\item~\textit{odgi depth} describes node depth over graph and path positions (\S\ref{sec:metrics}).
\item~\textit{odgi degree} describes node degree over graph and path positions (\S\ref{sec:metrics}).
\end{itemize}

@@

% \end{thebibliography}
\clearpage
\beginsupplement

>>>>

\newcommand{\vocab}{\textbf}
\newcommand{\red}[1]{{\textcolor{Red}{#1}}}
\newcommand{\FIXME}[1]{\red{[FIXME: #1]}}
\newcommand{\REVIEWED}[1]{{\textcolor{Red}{#1}}}
\newcommand{\beginsupplement}{%
    \renewcommand{\thesection}{S}
	\setcounter{table}{0}
	\renewcommand{\thetable}{S\arabic{table}}%
	\setcounter{figure}{0}
	\renewcommand{\thefigure}{S\arabic{figure}}%
}

@@

\address{
$^{\text{\sf 1}}$Genomics Research Centre, Human Technopole, Viale Rita Levi‑Montalcini 1, Milan, 20157, Italy \\
$^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, 72076, Germany \\
$^{\text{\sf 3}}$Biomedical Data Science, Dept. of Computer Science, University of T\"ubingen, T\"ubingen, Germany, 72076 \\
$^{\text{\sf 4}}$Department of Genetics, Genomics and Informatics, University of Tennessee Health Science Center, Memphis, 38163, Tennessee, USA
}

@@

%\FIXME{Update the references to the sections.}
\begin{itemize}
\item~\textit{odgi build} constructs the ODGI data model from GFA file (\S\ref{sec:build}).
\item~\textit{odgi view} converts the ODGI data model into GFA file (\S\ref{sec:build}).
\item~\textit{odgi viz} provides a linear visualization of the graph (\S\ref{sec:viz}).
\item~\textit{odgi draw} renders a 2D image of the graph (\S\ref{sec:viz}).
\item~\textit{odgi extract} excerpts subsets of the graph based on path ranges (\S\ref{sec:supp_edit}).
\item~\textit{odgi explode} breaks the graph into connected components (\S\ref{sec:supp_edit}).
\item~\textit{odgi squeeze} unifies disjoint graphs (\S\ref{sec:supp_edit}).
\item~\textit{odgi chop} breaks long nodes into shorter ones (\S\ref{sec:supp_edit}).
\item~\textit{odgi unchop} combines unitig nodes (\S\ref{sec:supp_edit}).
\item~\textit{odgi break} removes cycles in the graph (\S\ref{sec:supp_edit}).
\item~\textit{odgi prune} removes complex regions (\S\ref{sec:supp_edit}).
\item~\textit{odgi groom} resolves spurious inverting links (\S\ref{sec:supp_edit}).
\item~\textit{odgi position} lifts coordinates between path and graph positions (\S\ref{sec:untangle}).%
%\item \textit{odgi server} provides a HTTP server to lift coordinates (\S\ref{sec:untangle}).
\item~\textit{odgi untangle} deconvolutes paths relative to a reference (\S\ref{sec:untangle}).
\item~\textit{odgi tips} finds path end points relative to a reference (\S\ref{sec:supp_navigation}).
\item~\textit{odgi sort} orders the graph nodes (\S\ref{sec:sort}).
\item~\textit{odgi layout} establishes a 2D layout (\S\ref{sec:sort}).
\item~\textit{odgi matrix} derives the pangenome matrix (\S\ref{sec:supp_metrics}).
\item~\textit{odgi paths} lists and extracts paths in FASTA (\S\ref{sec:supp_metrics}).
\item~\textit{odgi flatten} converts the graph to FASTA and BED (\S\ref{sec:supp_metrics}).
\REVIEWED{\item~\textit{odgi pav} computes presence-abscence variations (\S\ref{sec:supp_metrics}).}
\item~\textit{odgi stats} provides numerical properties of the graph (\S\ref{sec:metrics}).
\item~\textit{odgi bin} generates a summarized view of the graph (\S\ref{sec:supp_metrics}).
\item~\textit{odgi depth} describes node depth over graph and path positions (\S\ref{sec:metrics}).
\item~\textit{odgi degree} describes node degree over graph and path positions (\S\ref{sec:metrics}).
\end{itemize}

@@

% \end{thebibliography}
\clearpage
\setcounter{page}{1}

\beginsupplement
